Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-25 VMCAI-revised-version/final.tex
up

Indeed, the structural termination problem consists in deciding if %the termination problem holds for 
a system terminates on every initial state. 
Since termination is w.l.o.g. reachability of $q_f({\bf 0})$ \mathieu{est-ce qu'on a pas besoin d'une hypothèse d'être deterministic ici pour que ce soit vraiment w.l.o.g. ??} for some control state $q_f$, we can formulate the structural termination problem as

\problemx{Structural termination}
{A reset-VASS $V=(Q,T)$ of dimension $d$, a control state $q_f \in Q$.}
{ $Q \times \N^d \longrightarrow^{*} q_f({\bf 0})$ ? \\}

@@

\mathieu{GOTO}

@@

\nocite{araki1976PN,dufourd1998reset}
\iffalse
\begin{proof}
{\sc Resilience} when $\Safe= \{ q_f({\bf 0}) \}$ for some state $q_f$ is equivalent to
deciding structural termination of reset-VASS, which is undecidable.
\qed \end{proof}
\fi

@@

%
Remark that the quantification over the path is existential rather than universal i.e. 
{\em zero-reachability}
does not asks that zero remains reachable from an initial state $s_0$ at all times but rather, that there exists at least one way to reach it.
Despite this it is possible to reduce 
the {\em zero-reachability problem} 
to
{\sc $t$-liveness}.
The following Proposition is a variation  to reset-VASS of Theorem~5.5 in \cite{peterson1981petri} originally stated for Petri nets, whose proof can be seen in Appendix~\ref{appendix}%
.
\begin{proposition}\label{liveness reset}
The  zero reachability problem can be reduced to {\sc $t$-liveness}.
\end{proposition}

@@

We now consider the case $\Safe = \mathop{\downarrow} \Safe$.
%
Unfortunately {\sc State-resilience} is undecidable in this case. As for {\sc Resilience} in WSTS when $\Safe = \mathop{\downarrow} \Safe$, this stems from undeciability of the 
structural termination of reset-VASS.
\mathieu{GOTO}

>>>>

Indeed, the structural termination problem consists in deciding if %the termination problem holds for 
a system terminates on every initial state.

\problemx{Structural termination}
{A reset-VASS $V=(Q,T)$ of dimension $d$.}
{ %$Q \times \N^d \longrightarrow^{*} q_f({\bf 0})$ ? 
Do all runs for every initial state terminate ?\\}

@@

% \mathieu{GOTO}

@@

\begin{proof}
\nocite{araki1976PN,dufourd1998reset}
{\sc Resilience} when $\Safe= \{ q_f({\bf 0}) \}$ for some state $q_f$ is equivalent to
deciding structural termination of reset-VASS,
since termination is w.l.o.g. reachability of $q_f({\bf 0})$ 
 \mathieu{est-ce qu'on a pas besoin d'une hypothèse d'être deterministic ici pour que ce soit vraiment w.l.o.g. ??} 
for some control state $q_f$. \qed \end{proof}

@@

% 
{\sc Resilience} (and {\sc $t$-liveness}) needs a set (resp. a transition) to always remains reachable (resp. fireable), while
{\em zero-reachability} concerns itself only with the existence of at least one way to reach some state $q(\textbf{0})$,
which could be unreachable from other reachable states. 
%
Despite this it is possible to reduce 
the {\em zero-reachability problem} 
to
{\sc $t$-liveness}.
The following Proposition is a variation  to reset-VASS of Theorem~5.5 in \cite{peterson1981petri} originally stated for Petri nets, whose proof can be seen in Appendix~\ref{appendix}%
.
\begin{proposition}\label{liveness reset}
The  zero reachability problem can be reduced to {\sc $t$-liveness}.
\end{proposition}

@@

We now consider the case $\Safe = \mathop{\downarrow} \Safe$.
%
Unfortunately {\sc State-resilience} is undecidable in this case. As for {\sc Resilience} in WSTS when $\Safe = \mathop{\downarrow} \Safe$, this stems from undeciability of the 
structural termination of reset-VASS.
%\mathieu{GOTO}
